### 2023-03-24 resilience.tex
up
details

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two finite sets: $\Bad$ and $\Safe$.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

\begin{proof}
Let $\Bad=\{J_1, J_2,...,J_n\}$ be the ideal decomposition of $\Bad$ and $B_{\Safe}=\{b_1,b_2,...,b_m\}$ be the minimal basis of $\Safe$.
The %uniform 
resilience problem (RP) is equivalent to an infinite number of instances of the coverability problem : for all $x \in \Bad$ does there exist an $j$ such that $b_j$ is coverable from $x$. This infinite set of coverability questions can be reduced to $n$ instances of the coverability problem in the completion $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ of $\mathscr{S}=(S,\rightarrow, \leq)$.

@@

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_a \mid a=1,..,m \times n)$
 % \alain{comment trouver les $k_a$ ?} 
 by iteratively checking the different possibles values of every $k_a$ until we find the right one,
 and we deduce that  $\mathscr{S}$ is $K$-resilient,
%  \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ? il pourrait exister un $K' \geq K$ pour lequel $\mathscr{S}$ est K'-resilient....}. 
else if some of these $n \times m$ coverability questions are negative then resilience
do not hold and bounded resilience do not hold either.
 Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (RP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}

>>>>

\begin{theorem}\label{down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and two finite \alain{non, confusion entre ensemble et base} sets: $\Bad$ and $\Safe$.
The resilience problem (RP) and the bounded resilience problem (BRP) are decidable.
\end{theorem}

\begin{proof}
Let $\{J_1, J_2,...,J_n\}$ be the ideal decomposition of $\Bad$ and $B_{\Safe}=\{b_1,b_2,...,b_m\}$ be the minimal basis of $\Safe$.
The %uniform 
resilience problem (RP) is equivalent to an infinite number of instances of the coverability problem : for all $x \in \Bad$ does there exist an $j$ such that $b_j$ is coverable from $x$. This infinite set of coverability questions can be reduced to a finite number of instances of the coverability problem in the completion $\hat{\mathscr{S}}=(Ideals(S),\rightarrow, \subseteq)$ of $\mathscr{S}=(S,\rightarrow, \leq)$.

@@

To decide the  bounded resilience problem (BRP), we decide $n \times m$ coverability questions: is state $b_j$ coverable from ideal $J_i$ ? If all these $n \times m$ coverability questions are positive then we compute $K=max(k_{i,j} \mid i=1,..,m $ and $j= 1,..m)$ where $k_{i,j}$ is the least length of a sequence that covers  $b_j$ from $J_i$.
\alain{peut-être definir $K_{ \mathscr{S}}(Safe,Bad)$ en dehors de la preuve comme suit: If all these $n \times m$ coverability questions are positive then  $K(Safe,Bad)=max(k_{i,j})$ else $K=\infty$}
 % \alain{comment trouver les $k_a$ ?} 
 by iteratively checking the different possibles values of every $k_a$ until we find the right one,
 and we deduce that  $\mathscr{S}$ is $K$-resilient,
%  \alain{else $\mathscr{S}$ is not $K$-resilient...et alors qu'en déduit-on ? il pourrait exister un $K' \geq K$ pour lequel $\mathscr{S}$ est K'-resilient....}. 
else if some of these $n \times m$ coverability questions are negative then resilience
do not hold and bounded resilience do not hold either.
 Since coverability is decidable for completion-post-effective $\omega^2$-WSTS, we have shown that both the 
  resilience problem (RP) and the  
  bounded resilience problem (BRP) are decidable.
\end{proof}
